Current State of Knowledge Representation Systems for Robotics

### 2011-11-22 paper.tex
Formatting in the PEIS section

\subsection{PEIS Ecology}
\label{sect|peis-ecology}

Reference paper:~\cite{Daoutis2009}

@@

Each PEIS component is running a \emph{PEIS Kernel} instance. Communication
between instance relies on a custom P2P communication protocol.

More in details:
- object identification based on viewpoint independent SIFT features
- formalized anchoring system that explicitely match percieved attributes to predicates
- Cyc predicates
- ground 12 colors, based on a paper on color perception. Could be useful for us.
- idem, they cite a paper on what spatial relations to compute
- location of objects based on a previously provided semantic map (but not much on this semantic map)
- two "memories": the robot memory stores the current list of percieved objects ; the archive memory stores what is not percieved anymore
- uses directly Cyc (ie, 250 000 common sense concepts...), via CycL language -> 2nd and higher order logics (quantification over predicates, functions, etc)
Remark: using 2nd order logic (ie meta statements), it would be easy to store the knowledge of each agent
- disambiguation in concept name by asking human to decide amongst all concepts known by Cyc
- template based natural language
- experiment conducted in a "smart" indoor environmement + simple robot

>>>>

\subsection{PEIS KR\&R}
\label{sect|peis-ecology}

@@

Each PEIS physical component is running a \emph{PEIS Kernel} instance. Communication
between instance relies on a custom P2P communication protocol.

The PEIS architecture allows for adding new abilities through software components sharing the common \emph{tuple space}.

We survey here the semantic layer~\cite{Daoutis2009}, referred as \emph{PEIS KR\&R}, that includes symbolic representation and reasoning.

% More in details:
% - object identification based on viewpoint independent SIFT features
% - formalized anchoring system that explicitely match percieved attributes to predicates
% - Cyc predicates
% - ground 12 colors, based on a paper on color perception. Could be useful for us.
% - idem, they cite a paper on what spatial relations to compute
% - location of objects based on a previously provided semantic map (but not much on this semantic map)
% - two "memories": the robot memory stores the current list of percieved objects ; the archive memory stores what is not percieved anymore
% - uses directly Cyc (ie, 250 000 common sense concepts...), via CycL language -> 2nd and higher order logics (quantification over predicates, functions, etc)
% Remark: using 2nd order logic (ie meta statements), it would be easy to store the knowledge of each agent
% - disambiguation in concept name by asking human to decide amongst all concepts known by Cyc
% - template based natural language
% - experiment conducted in a "smart" indoor environmement + simple robot
